*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-01-25 supplement.qmd
fix colors for all plots to keep temp, sal similar

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false
